Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-07-01 snapshot_system/snapshot.tex
updated references and added content linking text to figures.

The overall deduplication efficiency of VC is
\[
\frac{ (1-\delta) + \delta (\frac{m*C}{D*E})^{1-\alpha}}
{ 1- \frac{c_u}{c} }.
\]
where $(\frac{m*C}{D*E})^{1-\alpha}$ represents the percentage of the remaining chunks detected as duplicates
after inner VM deduplication. 
%Then the deduplication efficiency of CDS approach using top k most popular fingerprints is:
%\begin{equation}
%  e_k = (\frac{m*B}{F*D})^{1-\alpha}
%\end{equation}

@@

As illiustrated in Figure~\ref{fig-vo-links},
when the number of machines at each cluster increases, the number of total VMs increases.
Then $k$ increases since more memory is available to host the popular chunks index.
But for each physical machine, the number of VMs remains the same, and thus
$D$ is  a constant. Then  the overall deduplication efficiency of VC remains
a constant.

>>>>

The overall deduplication efficiency of VC is
\[
\frac{ (1-\delta) + \delta (\frac{m*C}{D*E})^{1-\alpha}}
{ 1- \frac{c_u}{c} }.
\]
where $(\frac{m*C}{D*E})^{1-\alpha}$ represents the percentage of the remaining
chunks detected as duplicates after inner VM deduplication.
Figure~\ref{fig-cds-coverage} shows measured CDS coverage in our 35 VM dataset.
You can see from the graph that the coverage actually increases as the datasize
increases, which indicates that $\alpha$ increases with the datasize (a
fixed-$\alpha$ model would predict constant coverage). This makes the CDS even
more effective, as the coverage of the CDS increases as more data is added.
%Then the deduplication efficiency of CDS approach using top k most popular fingerprints is:
%\begin{equation}
%  e_k = (\frac{m*B}{F*D})^{1-\alpha}
%\end{equation}

@@

As illustrated in Figure~\ref{fig-vo-links}\emph{I am not sure where this reference should point, but I don't think it is pointing to the right figure},
when the number of machines at each cluster increases, the number of total VMs increases.
Then $k$ increases since more memory is available to host the popular chunks index.
But for each physical machine, the number of VMs remains the same, and thus
$D$ is  a constant. Then  the overall deduplication efficiency of VC remains
a constant.
